Deterministic Scheduling of Periodic Messages in a Network

### 2017-07-17 article/article.tex

  When the waiting times are zero, $MT({\cal M})$ is equal to twice the lenght of the longest route, thus $T_{max}$ is not relevant anymore. For a route $r$, choosing the offset $m_r$ also sets the offset of the route $\rho(r)$ to $m_{r} + \lambda(r) \mod P$.
  Consider an assignment $\{m_0,\dots,m_{n-1}\}$ of a star routed network and let $m_i'= m_{i} - t(c_s,r_i) \mod P$.
  Then $\{m_0',\dots,m_{n-1}'\}$ is an assignment of the same star routed network where the weights of the arcs from $s_i$ to $c_s$ are $0$
  for all $i$. Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.

>>>>

  When the waiting times are zero, $MT({\cal M})$ is equal to twice the length of the longest route, thus $T_{max}$ is not relevant anymore. For a route $r$, choosing the offset $m_r$ also sets the offset of the route $\rho(r)$ to $m_{\rho(r)} = m_{r} + \lambda(r) \mod P$.
  Consider an assignment $(m_0,\dots,m_{n-1})$ of a star routed network and let $m_i'= m_{i} - t(c_s,r_i) \mod P$.
  Then $\{m_0',\dots,m_{n-1}'\}$ is an assignment of the same star routed network where the weights of the arcs from $s_i$ to $c_s$ are $0$ for all $i$. Therefore we assume from now on that the \emph{weight of the arcs from $s_i$ to $c_s$ are all equal to $0$}.
